Supplementary material

### 2018-06-07 Manuscript/ms.tex
Intro paragraph of discussion

Infectious diseases \cite{Ellner1998,Koelle2004} and ecological systems \cite{Bjornstad2001}, are often driven by the combined efforts of intrinsic non-linearities and feedbacks, seasonality, and stochasticity.
In this paper, we have highlighted the importance of these processes in driving the dynamics of dengue fever and shaping the relationship between mosquito abundance and human disease risk.

>>>>

Infectious diseases \cite{Ellner1998,Koelle2004} and ecological systems \cite{Bjornstad2001}, are often driven by the combined efforts of intrinsic non-linearities, seasonality, and stochasticity.
In the case of dengue fever, these processes can obscure the relationship between mosquito abundance and human disease.
We found that modeling temporary human immunity and seasonal variation in the mosquito mortality rate was able to effectively fit case reports and mosquito surveillance data from Vitoria, Brazil.
Control simulations using this model indicated that mosquito control was most effective at reducing the disease burden in a given year when implemented approximately 30 weeks prior to the start of that year, when the susceptible pool tends to be at a minimum.
Moreover, the effectiveness of control was strongly correlated with the period of cross-immunity, and the rate of turnover of the susceptible population.
Thus, human immunity appears to be a critical driver of the effectiveness of mosquito control.
